### 2022-06-27 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_betacov_mapping@cf5941efd35908a02185710410fc5afdf838af52 🚀

On closer inspection, these patterns recapitulate the evolutionary
history of both the order Chiroptera and the genus
\emph{Betacoronavirus}. Horseshoe bats (Rhinolophidae) are both the
reservoirs of the SARS-like viruses (subgenus \emph{Sarbecovirus}) and
the presumed ancestral host of
\emph{Betacoronavirus}.\textsuperscript{17} The hotspot of host richness
and viral diversity in southeast Asia---both of which are
disproportionately high, considering the global landscape of bat species
richness---is almost entirely driven by adaptive radiation in this
clade\textsuperscript{3,14}. In contrast, the Neotropical hotspot of
viral distinctiveness is the result of isolation by vicariance for both
bats and their viruses. Out of the four main groups of
betacoronaviruses, only the subgenus \emph{Merbecovirus} has been found
in animals in the Americas---an introduction that is generally presumed
to be ancient. While comparatively understudied, New World
merbecoviruses have been found in the ghost-faced bats (Mormoopidae),
New World leaf-nosed bats (Phyllostomidae), and free-tailed bats
(Molossidae) (add cite: Olival 2020 PLoS Pathogens). The former two
groups are endemic to the Neotropics, while the latter two and
particularly the phyllostomids are responsible for the hotspot of bat
diversity in the Amazon. Together, these groups play host to a distinct
regime of bat-betacoronavirus coevolution in the Americas.

>>>>

On closer inspection, these patterns recapitulate the evolutionary
history of both the order Chiroptera and the genus
\emph{Betacoronavirus}. Horseshoe bats (Rhinolophidae) are both the
reservoirs of the SARS-like viruses (subgenus \emph{Sarbecovirus}) and
the presumed ancestral host of
\emph{Betacoronavirus}.\textsuperscript{17} The hotspot of host richness
and viral diversity in southeast Asia---both of which are
disproportionately high, considering the global landscape of bat species
richness---is almost entirely driven by viral adaptive radiation through
host switching within this clade\textsuperscript{3,14}. In contrast, the
Neotropical hotspot of viral distinctiveness is driven by isolation by
host vicariance. Out of the four main groups of betacoronaviruses, only
the subgenus \emph{Merbecovirus} (MERS-like viruses) has been found in
animals in the Americas---an introduction that is generally presumed to
be ancient.\textsuperscript{3} While comparatively understudied, New
World merbecoviruses have been found in the ghost-faced bats
(Mormoopidae), New World leaf-nosed bats (Phyllostomidae), and
free-tailed bats (Molossidae) (add cite: Olival 2020 PLoS Pathogens).
The former two groups are endemic to the Neotropics, while the explosive
adaptive radiations of the latter two (and particularly the
phyllostomids) are responsible for the hotspot of bat diversity in the
Amazon. Together, these clades of New World bats play host to a distinct
regime of betacoronavirus coevolution.
